### 2022-08-13 doc/src/MSLevel.tex

>>>>

When the hypervisor extension is implemented, if a bit is
zero in the same position in both \z{mideleg}/\z{midelegh}
and \z{mvien}/\z{mvienh}, then that bit is read-only zero in
\z{hideleg}/\z{hidelegh} (in addition to being read-only zero
in \z{sip}/\z{siph}, \z{sie}/\z{sieh}, \z{hip}, and \z{hie}).
But if a bit for one of interrupts 13--63 is a one in
either \z{mideleg}/\z{midelegh} or \z{mvien}/\z{mvienh},
then the same bit in \z{hideleg}/\z{hidelegh} may be writable
or may be read-only zero, depending on the implementation.
No bits in \z{hideleg}/\z{hidelegh} are ever read-only ones.
The {\RISCV} Privileged Architecture further
constrains bits 12:0 of \z{hideleg}.
